% cv/cv.tex (ATS-friendly, 1-page priority)
\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.55cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\begin{document}

% ===== Header =====
\begin{minipage}[t]{0.72\textwidth}
{\LARGE \textbf{Chi Xiao}}\\
Linköping, Sweden \quad \href{mailto:xiao0600@gmail.com}{xiao0600@gmail.com}\\
\href{https://github.com/chi0600}{github.com/chi0600} \quad
\href{https://orcid.org/0009-0005-1562-0637}{ORCID: 0009-0005-1562-0637}
\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}
\raggedleft
Last updated:\\
\today
\end{minipage}

% ===== Summary =====
\section*{Summary}
\begin{itemize}
  \item System Developer (Telecom) and Industrial PhD researcher (Software Engineering / AI).
  \item Study driver for capacity and scalability assessments in telecom systems under high load.
  \item Research: reproducible evaluation and verification of LLM-generated artifacts (text, code, structured specifications).
\end{itemize}

% ===== Experience =====
\section*{Experience}
\textbf{Ericsson AB} — System Developer \hfill Sep 2021 -- Present \\
Linköping, Sweden
\begin{itemize}
  \item Study driver for capacity and scalability evaluations in telecom systems under high load.
  \item Own and maintain requirements and technical specifications; lead reviews and ensure consistency and traceability.
  \item Plan and analyze trials to validate large-scale user targets and performance trade-offs; align findings with stakeholders.
\end{itemize}

\textbf{Linköping University} — Research Engineer \hfill May 2019 -- Apr 2021 \\
Sweden
\begin{itemize}
  \item Worked on lab-on-chip devices for smartphone-based imaging surface plasmon resonance (iSPR) detection.
\end{itemize}

\textbf{Chengdu Yingnuo Industry Co., Ltd.} — Optical Engineer \hfill Apr 2017 -- Apr 2019 \\
China
\begin{itemize}
  \item Optical inspection for defect detection; imaging and data analysis.
  \item Built data processing and analysis scripts in MATLAB and C++.
\end{itemize}

% ===== Education =====
\section*{Education}
\textbf{Eindhoven University of Technology} — Industrial PhD \hfill Sep 2024 -- Present \\
Topic: Generative AI for software engineering (industrial PhD)

\textbf{Imperial College London} — M.Sc. Optics and Photonics \hfill 2015 -- 2016

\textbf{Jinan University} — B.Eng. Information Engineering \hfill 2011 -- 2015


% ===== Publications (Selected) =====
\section*{Publications (Selected)}
\begin{itemize}
  \item Chi Xiao et al. \textit{UML Sequence Diagram Generation: A Multi-Model, Multi-Domain Evaluation.} ICSE-SEIP 2025.
  \item Chi Xiao et al. \textit{A portable smartphone-based imaging surface plasmon resonance biosensor for allergen detection in plant-based milks.} Talanta, 2023.
  \item Chi Xiao et al. \textit{Print-and-stick unibody microfluidics coupled SPR chip for smartphone imaging SPR.} Analytica Chimica Acta, 2022.
\end{itemize}

% ===== Skills =====
\section*{Skills}
\textbf{Programming:} Python, C++, MATLAB \\
\textbf{Tools:} Git, Linux, Docker, SQL, GitHub Actions, LaTeX \\
\textbf{Engineering focus:} capacity/scalability analysis, test design, requirements/specifications, automation, stakeholder alignment

% ===== Awards =====
\section*{Awards}
Jinan University Scholarships (First Prize: 2012, 2014; Second Prize: 2013) \\
Honorable Mention, MCM/ICM

\end{document}
